---
title: "Violence Score"
output: html_notebook

purpose: In this notebook we explore the relations in the violence_score data and also further examine the people on the bottom edge of the age vs compas score pt cloud
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=F, message=F,echo = TRUE)
```

```{r}
library(tidyverse)
library(magrittr)
library(segmented)
source('functions.r')

load("Table_construction.Rdata") #loading beau's version of data
```

```{r}
features = features %>%
  # Add other useful information:
  inner_join(
    data_before %>% 
      select(person_id, screening_date, people) %>%
      unnest() %>%
      select(person_id, screening_date, race, sex, name),
    by = c("person_id","screening_date")
  ) %>%
  inner_join(features_on, by = c("person_id","screening_date")) %>%
  inner_join(outcomes, by = c("person_id","screening_date")) %>%
  
  # Create as many features as possible:
  mutate(
    raw_score = `Risk of Violence_raw_score`, # Adjust for violent/general
    decile_score = `Risk of Violence_decile_score`, # Adjust for violent/general
    p_juv_fel_count = pmin(p_juv_fel_count,2),
    p_felprop_violarrest = pmin(p_felprop_violarrest,5),
    p_murder_arrest = pmin(p_murder_arrest,3),
    p_felassault_arrest = pmin(p_felassault_arrest,3),
    p_misdemassault_arrest = pmin(p_misdemassault_arrest,3),
    #p_famviol_arrest = pmin(p_famviol_arrest,3),
    p_sex_arrest = pmin(p_sex_arrest,3),
    p_weapons_arrest = pmin(p_weapons_arrest,3),
    p_n_on_probation = pmin(p_n_on_probation,5),
    p_current_on_probation = pmin(p_current_on_probation,5),
    p_prob_revoke = pmin(p_prob_revoke,5),
    race_black = if_else(race=="African-American",1,0),
    race_white = if_else(race=="Caucasian",1,0),
    race_hispanic = if_else(race=="Hispanic",1,0),
    race_asian = if_else(race=="Asian",1,0),
    race_native = if_else(race=="Native American",1,0), # race == "Other" is the baseline
    
    # Subscales:
    vio_hist = p_juv_fel_count+
      p_felprop_violarrest+
      p_murder_arrest+
      p_felassault_arrest+
      p_misdemassault_arrest+
      #p_famviol_arrest+ #because no observations have nonzero for this
      p_sex_arrest+
      p_weapons_arrest,
    history_noncomp = p_prob_revoke+
      p_probation+p_current_on_probation+
      p_n_on_probation,
    
    # Filters (TRUE for obserations to keep)
    filt1 = `Risk of Recidivism_decile_score` != -1, `Risk of Violence_decile_score` != -1, # Filter 1
    filt3 = !is.na(current_offense_date), # Filter 3
    filt4 = current_offense_date <= current_offense_date_limit, # Filter 4
    filt5 = p_current_age > 18 & p_current_age <= 65,  # Filter 5
    filt6 = vio_hist == 0 , # Filter 6
    filt7 = history_noncomp==0 # Filter 7
  )
```



Risk of Violence
Modelled age with a 4th degree polynomial. See broward_sheriff_data for our efforts to model it with a variety of exponentials (couldn't get it quite right so used a polynomial in the end).
## Fit age polynomial

```{r}
features_age_poly = features %>%
  filter(filt1,filt5, filt6, filt7) 

lb_age = features_age_poly %>%
  group_by(p_current_age) %>%
  arrange(raw_score) %>%
  top_n(n=-1, wt=raw_score) # Fit lower bound on smallest value


mdl_age = lm(raw_score ~ 
               I(p_current_age^4) + 
               I(p_current_age^3) + 
               I(p_current_age^2) + 
               p_current_age, 
             data=lb_age)

# More precision for paper
summary(mdl_age)
print("Coefficients:")
sprintf("%.20e",mdl_age$coefficients) # More precision for paper

## Add f(age) to features and add filter
features = features %>%
  mutate(
    age_poly = predict(mdl_age, newdata=data.frame(p_current_age=p_current_age)),
    raw_score__age_poly = raw_score - age_poly,
    filt8 = raw_score >= age_poly - 0.05
  )

## Add same columns as above to lb_age 
lb_age = lb_age %>% 
    mutate(
    age_poly = predict(mdl_age, newdata=data.frame(p_current_age=p_current_age)),
    raw_score__age_poly = raw_score - age_poly,
    filt8 = raw_score >= age_poly - 0.05
    )
```

Plotting settings for age analysis
```{r}
xmin = 18
xmax = 65
xx = seq(xmin,xmax, length.out = 1000)
```

## Age polynomial plot
Generate a preliminary plot of age vs COMPAS violence score
```{r}
ggplot()+
  geom_point(aes(x=p_current_age, raw_score, color = factor(filt8)),alpha=.3, data=lb_age) +
  geom_line(aes(x=xx, predict(mdl_age, newdata=data.frame(p_current_age=xx))),color="#F8766D") +
  theme_bw()+
  xlim(xmin,xmax)+
  xlab("Age at COMPAS screening date") +
  ylab("Violent score") +
  theme(text = element_text(size=12),
        axis.text=element_text(size=12),
        legend.position="none")

ggplot()+
  geom_point(aes(x=p_current_age, raw_score), color="#619CFF",alpha=.3, data=features_age_poly) +
  geom_line(aes(x=xx, predict(mdl_age, newdata=data.frame(p_current_age=xx))),color="#F8766D") +
  theme_bw()+
  xlim(xmin,xmax)+
  xlab("Age at COMPAS screening date") +
  ylab("Violent score") +
  theme(text = element_text(size=12),
        axis.text=element_text(size=12),
        legend.position="none")
```

Filter out outliers under the age polynomial 
```{r}
features_age_poly2 = features %>% 
    filter(filt1, filt5, filt6, filt7, filt8)

lb_temp = features_age_poly2 %>%
  group_by(p_current_age) %>%
    arrange(raw_score)%>%
    top_n(n=-1, wt = raw_score)

lb_values = lb_temp %>%  
    select(p_current_age, raw_score)%>%
    group_by(p_current_age) %>%
      summarize(raw_score = unique(raw_score), 
                n_inds = n()) %>%
    arrange(p_current_age)

# valid_ages = lb_values %>% 
#     filter(n_inds > 1) %>%
#     select(p_current_age) %>% 
#     unlist() %>% as.numeric() 
# 
# lb_filt = lb_temp %>%
#   filter(p_current_age %in% valid_ages ) 

lb_filt = lb_temp 

#filtered out points 
lb_outliers = rbind(
                #reason not included in lb_filt was  
                #age not above age poly
                setdiff(lb_age, lb_temp) %>%
                  filter(!filt8) %>% #below age poly
                  mutate(reason = "Below age polynomial")
                
                # # reason not included in lb_filt was
                # # there was only a single value for that age
                # setdiff(lb_temp, lb_filt) %>%
                #   mutate(reason = "Only observation for a certain age")
                ) %>%
              select(p_current_age, p_age_first_offense, raw_score, reason)

lb = lb_filt %>% 
     select(p_current_age, p_age_first_offense, raw_score) %>%
     mutate(reason = "Used to construct linear splines") %>%
     rbind(lb_outliers)
```


Generating new age spline. 
```{r}
mdl_age_spline <- segmented(lm(raw_score ~ p_current_age, data = lb_filt), 
                            seg.Z = ~p_current_age, psi = list(p_current_age = c(22,36,58)),
  control = seg.control(display = FALSE)
)

#Add Filter 9
features = features %>%
  mutate(
    age_spline = predict(mdl_age_spline, newdata=data.frame(p_current_age=p_current_age)),
    raw_score__age_spline = raw_score - age_spline,
    filt9 = raw_score >= age_spline - 0.05
  )

```

Plottng individuals on new bottom edge produced by fitting to lb_filt individuals. 
```{r}
break1 =  summary.segmented(mdl_age_spline)$psi[1,2]
break2 = summary.segmented(mdl_age_spline)$psi[2,2]
break3 = summary.segmented(mdl_age_spline)$psi[3,2]

xx1 = seq(xmin,break1, length.out=500)
xx2 = seq(break1,break2, length.out=500)
xx3 = seq(break2,break3, length.out=500)
xx4 = seq(break3,xmax, length.out=500)

age_spline_viol = 
  ggplot()+
  geom_point(aes(x=p_current_age, raw_score, color= factor(reason)),alpha=.5, data=lb ) +
  scale_color_manual(values=c("red", "grey25")) + 
  geom_line(aes(x=xx1, y = predict(mdl_age_spline, newdata=data.frame(p_current_age=xx1))),
                color="#F8766D", size = 1) +
  geom_line(aes(x=xx2, y = predict(mdl_age_spline, newdata=data.frame(p_current_age=xx2))),
                color="darkorange1", size = 1) +
  geom_line(aes(x=xx3, y = predict(mdl_age_spline, newdata=data.frame(p_current_age=xx3))),
                color="cyan3", size = 1) +
  geom_line(aes(x=xx4, y = predict(mdl_age_spline, newdata=data.frame(p_current_age=xx4))),
                color="seagreen3", size = 1) +
  theme_bw()+
  xlim(xmin,xmax)+
  labs(
    x = "\n Age at COMPAS screening date", 
    y = "Violence Score \n"
  ) +
  theme(text = element_text(size=14),
        axis.text=element_text(size=14),
        legend.position = c(.95,.95),
        legend.title = element_blank(),
        # legend.key.width = unit(1.5, "cm"),
        legend.justification = c("right", "top"),
        legend.key = element_rect(fill = "aliceblue"),
        legend.background = element_rect(fill="aliceblue",
                                  size=0.5, linetype="solid")
        )
age_spline_viol
```

```{r}
ggsave("Figures/age_spline_viol.pdf",plot = age_spline_viol, width = 7, height = 4, units = "in")

```

Examining individuals in lb_filt where age at first offense != current age
```{r}

#plot of age at first offense != current age in red with inds in lb_filt
fireplot_lb_viol = ggplot()+
  geom_point(aes(x=p_current_age, y = raw_score,colour = p_current_age == p_age_first_offense ), 
             alpha=.3, data=lb_filt %>% na.omit()) +
  scale_colour_manual(name='Current age equal to age at first arrest', values = setNames(c('red','#619CFF'),c(F, T))) +
  theme_bw()+
  xlim(xmin,xmax)+
  xlab("\n Age at COMPAS screening date") +
  ylab("Violent score \n") +
  theme(text = element_text(size=14),
        axis.text=element_text(size=14), 
        legend.position ="top")
fireplot_lb_viol

#same plot as above but with everybody in features
fireplot_all_viol = ggplot()+
  geom_point(aes(x=p_current_age, y = raw_score, colour = p_current_age == p_age_first_offense ), 
             alpha=.2, data=features_age_poly2 %>% 
                            na.omit() %>%
                            mutate(p_current_age = ifelse(p_current_age == p_age_first_offense, 
                                                          p_current_age, 
                                                          p_current_age+.5))
             ) +
  scale_colour_manual(name='Current age equal to age at first arrest', values = setNames(c('red','#619CFF'),c(F, T))) +
  theme_bw()+
  xlim(xmin,xmax)+
  xlab("\n Age at COMPAS screening date") +
  ylab("Violent score \n") +
  theme(text = element_text(size=14),
        axis.text=element_text(size=14), 
        legend.position ="top")
fireplot_all_viol


#plot of score vs age at first arrest
age_first_offense_viol = ggplot()+
  geom_point(aes(x=p_age_first_offense, raw_score), color="#619CFF",alpha=.3, 
             data=features_age_poly2) +
  theme_bw()+
  xlim(xmin,xmax)+
  xlab("\n Age at First Offense") +
  ylab("Violent score \n") +
  theme(text = element_text(size=14),
        axis.text=element_text(size=14),
        legend.position="none")
age_first_offense_viol

#plot of score vs current age and age at first arrest
reverse_fireplot_all_viol = ggplot()+
  geom_point(aes(x=p_current_age, raw_score), color="#619CFF",alpha=.2, 
             data=features_age_poly2 %>% 
                  na.omit() %>%
                  mutate(p_current_age = p_current_age+0.5 )) +
  geom_point(aes(x=p_age_first_offense, raw_score), color="red",alpha=.04, 
             data=features_age_poly2) +
  scale_colour_manual(name='Legend', values = setNames(c('red','#619CFF'),c("Age at first offense", "Current age"))) +
  theme_bw()+
  xlim(xmin,xmax)+
  xlab("\n Age") +
  ylab("Violent score \n") +
  theme(text = element_text(size=14),
        axis.text=element_text(size=14),
        legend.position="none")
reverse_fireplot_all_viol

#Plotting people in lb, so that points which repeat more are larger. 
lb_inds_freq_viol = ggplot()+
  stat_sum(aes(x=p_current_age, raw_score), color="#619CFF",alpha=.7, data=lb_filt) +
  theme_bw() +
  xlim(xmin,xmax) +
  xlab("\n Age at COMPAS screening date") +
  ylab("Violent score\n ") +
  theme(text = element_text(size=14),
        axis.text=element_text(size=14),
        legend.position="none")
lb_inds_freq_viol


```


Save figures for paper
```{r}
ggsave("Figures/fireplot_all_viol.pdf",plot = fireplot_all_viol, width = 7, height = 4, units = "in")
ggsave("Figures/reverse_fireplot_all_viol.pdf",plot = reverse_fireplot_all_viol, width = 7, height = 4, units = "in")
ggsave("Figures/lb_inds_freq_viol.pdf",plot = lb_inds_freq_viol, width = 7, height = 4, units = "in")

```

### Age at first offense analysis


```{r}
#Filter observations to remove age outliers
features_age_spline = features %>% 
    filter(filt1, filt5, filt6, filt7,filt9)

ggplot()+
  geom_point(aes(x=p_age_first_offense, y= raw_score__age_spline), color = "#619CFF",alpha=.3, data=features_age_spline) +
  theme_bw()+
  xlim(xmin,xmax)+
  xlab("Age at First Offense") +
  ylab("Violence score - age spline") +
  theme(text = element_text(size=14),
        axis.text=element_text(size=14),
        legend.position="none")

```

### History of Violence Subscale Analysis

Plotting settings for history of violence subscale analysis
```{r}
xmin_vio_hist = 0
xmax_vio_hist = 13
xx_vio_hist = seq(xmin_vio_hist,xmax_vio_hist, length.out = 1000)
```


Plot violence history vs score after subtracting  out the age splines. 
```{r}
features_age_spline = features %>% 
    filter(filt1, filt5, filt9)

ggplot()+
  geom_point(aes(x=vio_hist, y= raw_score__age_spline), color = "#619CFF",alpha=.3, data=features_age_spline) +
  theme_bw()+
  xlim(xmin_vio_hist,xmax_vio_hist)+
  ylim(-1, 5) + 
  xlab("History of Violence Subscale Score ") +
  ylab("Violence score - f_age") +
  theme(text = element_text(size=14),
        axis.text=element_text(size=14),
        legend.position="none")

```

Iterate through possible subscale variable weights from 1 - 2, testing a higher weight of 3 on murder arrest and felony assault arrests. 


```{r}
weights = 
```

```{r}
for(var_weights in c(weights)){
  
  features_age_spline = features_age_spline %>%
        mutate(
          vio_hist_weighted = 
          var_weights[[1]] * p_juv_fel_count +
          var_weights[[2]] * p_felprop_violarrest +
          var_weights[[3]] * p_murder_arrest +
          var_weights[[4]] *  p_felassault_arrest +
          var_weights[[5]] * p_misdemassault_arrest +
          #p_famviol_arrest+ #because no observations have nonzero for this
          var_weights[[6]] * p_sex_arrest +
          var_weights[[7]] * p_weapons_arrest )
  
  print(
  ggplot()+
  geom_point(aes(x=vio_hist_weighted, y= raw_score__age_spline), color = "#619CFF",alpha=.3, data=features_age_spline) +
  theme_bw()+
  xlim(xmin_vio_hist,xmax_vio_hist)+
  ylim(-1, 5) + 
  xlab("History of Violence Subscale Score ") +
  ylab("Violence score - f_age") +
  theme(text = element_text(size=14),
        axis.text=element_text(size=14),
        legend.position="none")
  )
  

}


```


Examine Lower bound individuals, using filter 7 (noncomp history = 0)
```{r}

```

### History of Noncompliance Subscale Analysis
Plotting settings for history of violence subscale analysis
```{r}
xmin_history_noncomp = 0
xmax_history_noncomp = 21
xx_history_noncomp = seq(xmin_history_noncomp,xmax_history_noncomp, length.out = 1000)
```

Plot noncompliance history vs score
```{r}
ggplot()+
  geom_point(aes(x=history_noncomp, y= raw_score__age_spline), color = "#619CFF",alpha=.3, data=features_age_spline) +
  theme_bw()+
  xlim(xmin_history_noncomp,xmax_history_noncomp)+
  ylim(-1, 5) + 
  xlab("History of Noncompliance Subscale Score ") +
  ylab("Violence score - f_age") +
  theme(text = element_text(size=14),
        axis.text=element_text(size=14),
        legend.position="none")

```

####EXAMINING PEOPLE IN LB_INDS - for first age poly

Examining people in age_subset (bottom edge of age_poly_viol vs COMPAS score pt cloud) more closely
```{r}

ggplot(lb_filt, aes(x=vio_hist, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     theme_bw()+
     ggtitle("Risk of Violence Raw vs Summed violence history")

ggplot(lb_filt, aes(x=history_noncomp, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  + 
     theme_bw()+
     ggtitle("Risk of Violence Raw vs summed history of noncompliance")

```

Histograms displaying count of people in the age_subset with violence_history scores of "x" for the lower bound individuals, NOT filtering for a violence score of 0. 
```{r}

#history of violence histogram
ggplot(lb_inds, aes(x=vio_hist)) +
     geom_histogram()  +
     ggtitle("Distribution of Summed History of Violence Subscale Items\nfor Individuals on Lower Bound of age_poly")

#comparison histogram for all individuals who are 18-70, have scores not -1
ggplot(features%>%filter(filt1,filt5,filt8), 
       aes(x=vio_hist)) +
     geom_histogram()  +
     ggtitle("Distribution of Summed History of Violence Subscale Items\nfor All Individuals")


#history of noncompliance histogram
ggplot(lb_inds, aes(x=history_noncomp)) +
     geom_histogram()  +
     ggtitle("Distribution of Summed History of Noncompliance Subscale Items\nfor Individuals on Lower Bound of age_poly")

#comparison histogram for all individuals
ggplot(features%>%filter(filt1,filt5,filt8), 
       aes(x=history_noncomp)) +
     geom_histogram()  +
     ggtitle("Distribution of Summed History of Noncompliance Subscale Items\nfor All Individuals")

```


Question: of the crimes that people with a violence history of 1 or 2 committed, which ones were they?
(Did not ask same question for history of noncompliance because there was only 1 individual nonzero history of noncomp)
```{r}
age_subset_long=lb_inds%>%
               select(vio_hist,person_id,p_juv_fel_count,p_felprop_violarrest,
                      p_murder_arrest,p_felassault_arrest,
                      p_misdemassault_arrest,#p_famviol_arrest 
                      p_sex_arrest,p_weapons_arrest)%>%
               filter(vio_hist==2 | vio_hist==1)%>%
               gather(violence_history_component,component_count,p_juv_fel_count:p_weapons_arrest,factor_key = T)%>%
               group_by(vio_hist, violence_history_component)%>%
                  summarise(comp_sum = sum(component_count))


ggplot(age_subset_long, aes(x=violence_history_component, 
                            y=comp_sum,fill = as.character(vio_hist))) +
      geom_bar(stat="identity", position=position_dodge())+
      # geom_bar(stat="identity", fill = "steelblue")+
      ggtitle("Distribution of Violence History Subscale Items\nfor Individuals' Violence History") + 
      xlab("Components") + 
      ylab("Count of Components") + 
      scale_fill_discrete(name = "Violence history scores")+ 
      scale_fill_brewer(palette="Paired")+

      theme_minimal() + 
      theme(axis.text.x = element_text(angle = 45, vjust=1,hjust=1)) 

```



Exploring relationship between COMPAS score and variables other than age - 
OLD CODE USING OLD VARNAMES
```{r}
ggplot(features, aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Offense")

ggplot(poly_noage, aes(x=p_current_age, y=score_no_age)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw (No current age) vs Current Age")

ggplot(poly_noage, aes(x=p_age_first_offense, y=score_no_age)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Offense, no current age")

#checking the relationship b/w DISTANCE b/w ages, and score
ggplot(poly_noage, aes(x=p_current_age-p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Current Age-Age at First Offense")

ggplot(poly_noage, aes(x=p_current_age-p_age_first_offense, y=score_no_age)) +
     geom_point(shape=1)  +
     ggtitle("Corrected Score vs Current Age-Age at First Offense")

#looking at people at bottom edge of corrected score vs p_age_first_offense 
bottom_age1=train%>%
           group_by(p_age_first_offense)%>%
              arrange(`Risk of Violence_raw_score`-age_poly_viol(p_current_age),.by_group=TRUE)%>%
              top_n(n=-1,wt=`Risk of Violence_raw_score`)

ggplot(bottom_age1, aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`-age_poly_viol(p_current_age))) +
     geom_point(shape=1)  

#looking at people in age_subset (bottom edge of age vs raw violence score relationship) and plotting against age_first_offense instead
ggplot(lb_inds, aes(x=p_current_age, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at Current Offense, age_subset")

ggplot(lb_inds, aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Offense, age_subset")

```



Trying to see the relationship between age at first offense and score, by looking at people who have only age contributing to their score (or as much so as possible)
```{r}
offense1=train%>%
          group_by(p_current_age)%>%
              arrange(`Risk of Violence_raw_score`,.by_group=TRUE)%>%
              top_n(n=-5,wt=`Risk of Violence_raw_score`)%>%
              ungroup()%>%
          filter(p_felony_count_person==0&(cq_fail_appear_two_yr+cq_fail_appear_two_plus)==0)


ggplot(offense1, aes(x=p_current_age, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     geom_point(data=lb_inds, aes(x=p_current_age, y=`Risk of Violence_raw_score`),shape=1, color="red") +
     ggtitle("Risk of Violence Raw vs Age at Current Offense, offense1")

for(age in (18:60)){
  
  print(
    ggplot(filter(offense1, p_current_age==age) , aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle(paste0("age=",age, ", offense1"))
  )
  
}

offense2=train%>%
          filter(p_felony_count_person==0&(cq_fail_appear_two_yr+cq_fail_appear_two_plus)==0
                 &p_current_age>40&p_age_first_offense<30)

ggplot(offense2, aes(x=p_current_age, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     geom_point(data=lb_inds, aes(x=p_current_age, y=`Risk of Violence_raw_score`),shape=1, color="red") +
     ggtitle("Risk of Violence Raw vs Age at Current Offense, offense1")

ggplot(offense2, aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Offense, offense1")

for(age in (18:60)){
  print(
    ggplot(filter(offense2, p_current_age==age) , aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle(paste0("age=",age, ", offense1"))
  )
  
}

```


Same as above, but with p_age_first_arrest
```{r}
ggplot(train, aes(x=p_age_first_arrest, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Arrest")

ggplot(poly_noage, aes(x=p_current_age, y=score_no_age)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw (No current age) vs Current Age")

ggplot(poly_noage, aes(x=p_age_first_arrest, y=score_no_age)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Arrest, no current age")

#checking the relationship b/w DISTANCE b/w ages, and score
ggplot(poly_noage, aes(x=p_current_age-p_age_first_arrest, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Current Age-Age at First Arrest")

ggplot(poly_noage, aes(x=p_current_age-p_age_first_arrest, y=score_no_age)) +
     geom_point(shape=1)  +
     ggtitle("Corrected Score vs Current Age-Age at First Arrest")

first_arrest_low=train%>%
                   mutate(score_no_age=`Risk of Violence_raw_score`-age_poly_viol(p_current_age))%>%
                   # filter(p_age_first_arrest<=20)%>%
                   filter(p_current_age!=p_age_first_arrest)%>%
                   filter(p_felprop_violarrest==0&p_misdemassault_arrest<=3&p_felassault_arrest==0
                          &p_murder_arrest==0&p_famviol_arrest==0&p_sex_arrest==0
                          &p_yrs5_felcount_person<=1&p_misdem_count_5yrs<=3&cq_fail_appear_two_yr<=3)

ggplot(first_arrest_low, aes(x=p_age_first_arrest, y=`Risk of Violence_raw_score`))+
  geom_point(shape=1)+
  ggtitle("Raw Score vs p_age_first_arrest, xlim<=20, no age=age@ first arrest")

ggplot(first_arrest_low, aes(x=p_age_first_arrest, y=score_no_age))+
  geom_point(shape=1)+
  ggtitle("Corrected Score vs p_age_first_arrest, xlim<=20, no age=age@ first arrest")
```


```{r}
ggplot(train, aes(x=p_yrs5_trafcount_person, y=`Risk of Violence_raw_score`-age_poly_viol(p_current_age)))+
  geom_point(shape=1)+
  ggtitle("Corrected Score vs 5 Yr Traffic")

#xlim to 3 b/c can only log on compas assessment as 0,1,2,3+
ggplot(train, aes(x=p_felassault_arrest, y=`Risk of Violence_raw_score`-age_poly_viol(p_current_age)))+
  geom_point(shape=1)+
  xlim(0,5)+ ylim(-1.5,3)+
  ggtitle("Corrected Score vs p_felassault_arrest")


```

