---
title: "Violence Score"
output: html_notebook

purpose: In this notebook we explore the relations in the violence_score data and also further examine the people on the bottom edge of the age vs compas score pt cloud
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=F, message=F,echo = TRUE)
```

```{r}
library(tidyverse)
library(magrittr)

load("Table_construction.Rdata") #loading beau's version of data

age_poly_viol =function(x){ 0.000000407808994851*x^4 - 0.000088176770770443*x^3 + 0.007436939324225960*x^2 - 0.316106532730131000*x + 1.553988869973560000}

features_filt = features_before_on %>%
  inner_join(
    data_before %>% 
      select(person_id, screening_date, people) %>%
      unnest() %>%
      select(person_id, screening_date, race, sex, name),
    by = c("person_id","screening_date")
  ) %>%
  inner_join(features_on, by = c("person_id","screening_date")) %>%
  inner_join(outcomes, by = c("person_id","screening_date")) %>%
  filter(`Risk of Recidivism_decile_score` != -1, `Risk of Violence_decile_score` != -1) %>% # Filter 1
  filter(!is.na(current_offense_date)) %>% # Filter 3
  filter(screening_date <= current_offense_date_limit) %>% # Filter 4
  mutate(recid_use = as.factor(recid_violent), 
         # Select recidivism or violent recidivism to use in this script 
         decile_use = `Risk of Violence_decile_score`) %>%
        # Select recidivism or violent recidivism decile score to use in this script
  filter(p_current_age>18 & p_current_age<=70) %>% #filter 5, age filter
  filter(`Risk of Violence_raw_score` >= age_poly_viol(p_current_age) ) #filter age outliers (people beneath the age poly)
   
#round the count train 
train = features_filt %>%
  mutate(
    #p_current_age,
    p_age_first_offense,
    p_juv_fel_count = pmin(p_juv_fel_count,2),
    p_felprop_violarrest = pmin(p_felprop_violarrest,5),
    p_murder_arrest = pmin(p_murder_arrest,3),
    p_felassault_arrest = pmin(p_felassault_arrest,3),
    p_misdemassault_arrest = pmin(p_misdemassault_arrest,3),
    #p_famviol_arrest = pmin(p_famviol_arrest,3), #there are none
    p_sex_arrest = pmin(p_sex_arrest,3),
    p_weapons_arrest = pmin(p_weapons_arrest,3),
    p_n_on_probation = pmin(p_n_on_probation,5),
    p_current_on_probation = pmin(p_current_on_probation,5),
    p_prob_revoke = pmin(p_prob_revoke,5),
    violence_history=p_juv_fel_count+p_felprop_violarrest+
                    p_murder_arrest+p_felassault_arrest+
                    p_misdemassault_arrest +#p_famviol_arrest +
                    p_sex_arrest+p_weapons_arrest,
    history_noncomp=p_prob_revoke+p_probation+p_current_on_probation+p_n_on_probation,
    violence_remainder=`Risk of Violence_raw_score`-age_poly_viol(p_current_age))

```


Risk of Violence
Modelled age with a 4th degree polynomial. See broward_sheriff_data for our efforts to model it with a variety of exponentials (couldn't get it quite right so used a polynomial in the end).
```{r}

age_subset=train%>%
           filter(p_current_age>18&p_current_age<=70)%>%
           group_by(p_current_age)%>%
              arrange(`Risk of Violence_raw_score`,.by_group=TRUE)%>%
              top_n(n=-1,wt=`Risk of Violence_raw_score`)
# write.csv(age_subset, 'age_violence_score.csv')

ggplot(train, aes(x=p_current_age, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Age at Current Screening vs COMPAS Violent\nRecidivism Score (modelled w/deg4 polynomial)") +
     stat_function(fun = age_poly_viol, colour="blue",size=1.3) +  
     xlim(18,70)+
     xlab("Age at Current Screening") +
     ylab("Risk of Violent Recidivism Raw") +
     theme(text=element_text(size=18),
           axis.ticks=element_line(size=1),
           axis.ticks.length = unit(3, "mm"))
  

```



Examining people in age_subset (bottom edge of age_poly_viol vs COMPAS score pt cloud) more closely
```{r}
#confirming that we have selected the "lower bound" observations
ggplot(age_subset, aes(x=p_current_age, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at Current Offense, age_subset")

ggplot(age_subset, aes(x=violence_history, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at Current Offense, age_subset")

ggplot(age_subset, aes(x=history_noncomp, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at Current Offense, age_subset")

ggplot(age_subset, aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Offense, age_subset")


```


Histograms displaying count of people in the age_subset with violence_history scores of "x"
```{r}

#history of violence histogram
ggplot(age_subset, aes(x=violence_history)) +
     geom_histogram()  +
     ggtitle("Distribution of Summed History of Violence Subscale Items\nfor Individuals on Lower Bound of age_poly")

#comparison histogram for all individuals
ggplot(train, aes(x=violence_history)) +
     geom_histogram()  +
     ggtitle("Distribution of Summed History of Violence Subscale Items\nfor All Individuals")


#history of noncompliance histogram
ggplot(age_subset, aes(x=history_noncomp)) +
     geom_histogram()  +
     ggtitle("Distribution of Summed History of Noncompliance Subscale Items\nfor Individuals on Lower Bound of age_poly")

#comparison histogram for all individuals
ggplot(train, aes(x=history_noncomp)) +
     geom_histogram()  +
     ggtitle("Distribution of Summed History of Noncompliance Subscale Items\nfor All Individuals")

```
Histograms breaking down the distribution of subscale components for individuals on bottom edge (vs all individuals)
```{r}
#subset of 38 people
age_subset_long=age_subset%>%
               select(violence_history,person_id,p_juv_fel_count,p_felprop_violarrest,
                      p_murder_arrest,p_felassault_arrest,
                      p_misdemassault_arrest,#p_famviol_arrest 
                      p_sex_arrest,p_weapons_arrest)%>%
               filter(violence_history==2 | violence_history==1)%>%
               gather(violence_history_component,component_count,p_juv_fel_count:p_weapons_arrest,factor_key = T)%>%
               group_by(violence_history, violence_history_component)%>%
                  summarise(comp_sum = sum(component_count))


ggplot(age_subset_long, aes(x=violence_history_component, 
                            y=comp_sum,fill = as.character(violence_history))) +
      geom_bar(stat="identity", position=position_dodge())+
      # geom_bar(stat="identity", fill = "steelblue")+
      ggtitle("Distribution of Violence History Subscale Items\nfor Individuals' Violence History") + 
      xlab("Components") + 
      ylab("Count of Components") + 
      scale_fill_discrete(name = "Violence history scores")+ 
      scale_fill_brewer(palette="Paired")+

      theme_minimal() + 
      theme(axis.text.x = element_text(angle = 45, vjust=1,hjust=1)) 



```


Exploring relationship between COMPAS score and variables other than age
```{r}
ggplot(train, aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Offense")

ggplot(poly_noage, aes(x=p_current_age, y=score_no_age)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw (No current age) vs Current Age")

ggplot(poly_noage, aes(x=p_age_first_offense, y=score_no_age)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Offense, no current age")

#checking the relationship b/w DISTANCE b/w ages, and score
ggplot(poly_noage, aes(x=p_current_age-p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Current Age-Age at First Offense")

ggplot(poly_noage, aes(x=p_current_age-p_age_first_offense, y=score_no_age)) +
     geom_point(shape=1)  +
     ggtitle("Corrected Score vs Current Age-Age at First Offense")

#looking at people at bottom edge of corrected score vs p_age_first_offense 
bottom_age1=train%>%
           group_by(p_age_first_offense)%>%
              arrange(`Risk of Violence_raw_score`-age_poly_viol(p_current_age),.by_group=TRUE)%>%
              top_n(n=-1,wt=`Risk of Violence_raw_score`)

ggplot(bottom_age1, aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`-age_poly_viol(p_current_age))) +
     geom_point(shape=1)  

#looking at people in age_subset (bottom edge of age vs raw violence score relationship) and plotting against age_first_offense instead
ggplot(age_subset, aes(x=p_current_age, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at Current Offense, age_subset")

ggplot(age_subset, aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Offense, age_subset")

```



Trying to see the relationship between age at first offense and score, by looking at people who have only age contributing to their score (or as much so as possible)
```{r}
offense1=train%>%
          group_by(p_current_age)%>%
              arrange(`Risk of Violence_raw_score`,.by_group=TRUE)%>%
              top_n(n=-5,wt=`Risk of Violence_raw_score`)%>%
              ungroup()%>%
          filter(p_felony_count_person==0&(cq_fail_appear_two_yr+cq_fail_appear_two_plus)==0)


ggplot(offense1, aes(x=p_current_age, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     geom_point(data=age_subset, aes(x=p_current_age, y=`Risk of Violence_raw_score`),shape=1, color="red") +
     ggtitle("Risk of Violence Raw vs Age at Current Offense, offense1")

for(age in (18:60)){
  
  print(
    ggplot(filter(offense1, p_current_age==age) , aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle(paste0("age=",age, ", offense1"))
  )
  
}

offense2=train%>%
          filter(p_felony_count_person==0&(cq_fail_appear_two_yr+cq_fail_appear_two_plus)==0
                 &p_current_age>40&p_age_first_offense<30)

ggplot(offense2, aes(x=p_current_age, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     geom_point(data=age_subset, aes(x=p_current_age, y=`Risk of Violence_raw_score`),shape=1, color="red") +
     ggtitle("Risk of Violence Raw vs Age at Current Offense, offense1")

ggplot(offense2, aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Offense, offense1")

for(age in (18:60)){
  print(
    ggplot(filter(offense2, p_current_age==age) , aes(x=p_age_first_offense, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle(paste0("age=",age, ", offense1"))
  )
  
}

```


Same as above, but with p_age_first_arrest
```{r}
ggplot(train, aes(x=p_age_first_arrest, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Arrest")

ggplot(poly_noage, aes(x=p_current_age, y=score_no_age)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw (No current age) vs Current Age")

ggplot(poly_noage, aes(x=p_age_first_arrest, y=score_no_age)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Age at First Arrest, no current age")

#checking the relationship b/w DISTANCE b/w ages, and score
ggplot(poly_noage, aes(x=p_current_age-p_age_first_arrest, y=`Risk of Violence_raw_score`)) +
     geom_point(shape=1)  +
     ggtitle("Risk of Violence Raw vs Current Age-Age at First Arrest")

ggplot(poly_noage, aes(x=p_current_age-p_age_first_arrest, y=score_no_age)) +
     geom_point(shape=1)  +
     ggtitle("Corrected Score vs Current Age-Age at First Arrest")

first_arrest_low=train%>%
                   mutate(score_no_age=`Risk of Violence_raw_score`-age_poly_viol(p_current_age))%>%
                   # filter(p_age_first_arrest<=20)%>%
                   filter(p_current_age!=p_age_first_arrest)%>%
                   filter(p_felprop_violarrest==0&p_misdemassault_arrest<=3&p_felassault_arrest==0
                          &p_murder_arrest==0&p_famviol_arrest==0&p_sex_arrest==0
                          &p_yrs5_felcount_person<=1&p_misdem_count_5yrs<=3&cq_fail_appear_two_yr<=3)

ggplot(first_arrest_low, aes(x=p_age_first_arrest, y=`Risk of Violence_raw_score`))+
  geom_point(shape=1)+
  ggtitle("Raw Score vs p_age_first_arrest, xlim<=20, no age=age@ first arrest")

ggplot(first_arrest_low, aes(x=p_age_first_arrest, y=score_no_age))+
  geom_point(shape=1)+
  ggtitle("Corrected Score vs p_age_first_arrest, xlim<=20, no age=age@ first arrest")
```


```{r}
ggplot(train, aes(x=p_yrs5_trafcount_person, y=`Risk of Violence_raw_score`-age_poly_viol(p_current_age)))+
  geom_point(shape=1)+
  ggtitle("Corrected Score vs 5 Yr Traffic")

#xlim to 3 b/c can only log on compas assessment as 0,1,2,3+
ggplot(train, aes(x=p_felassault_arrest, y=`Risk of Violence_raw_score`-age_poly_viol(p_current_age)))+
  geom_point(shape=1)+
  xlim(0,5)+ ylim(-1.5,3)+
  ggtitle("Corrected Score vs p_felassault_arrest")


```


```{r}
data_num=train%>%
                select(person_id,`Risk of Violence_raw_score`,p_recid_raw,p_fail_to_appear_raw,
                       p_current_age,cq_fail_appear_two_yr,cq_fail_appear_two_plus,
                       p_yrs5_felcount_person, p_felony_count_person,cq_prior_conviction_F,
                       p_misdem_count_5yrs,p_misdem_count_person,cq_prior_conviction_M,
                       p_drug_count_5yrs,p_drug_count_person,
                       p_yrs5_trafcount_person,p_traffic_count_person,prior_conviction_T,
                       p_current_violent_offense,
                       p_prison_visits,p_prison_time,
                       p_jail_visits, p_jail_time,
                       cq_violent_conviction,
                       p_marital_status,p_sex,p_race,
                       p_numcases
                       )%>%
  
                mutate(corrected_age=age_poly_viol(p_current_age))

write.csv(data_num,"data_num.csv")

```


Comparing generated COMPAS score vs original compas score 
With subtracted off age scores 
```{r}
predicted_COMPAS=train%>%
                  mutate(total_fail_appear=cq_fail_appear_two_yr+cq_fail_appear_two_plus,
                         corrected_age=age_poly_viol(p_current_age)
)

#idea: limit the ranges of the variables in the history of violence scales to the multiple choice answers in the assessment
predicted_COMPAS_xlim=train%>%
                      mutate(total_fail_appear=cq_fail_appear_two_yr+cq_fail_appear_two_plus,
                             corrected_age=age_poly_viol(p_current_age),
                             p_felprop_violarrest=ifelse(p_felprop_violarrest>5,5,p_felprop_violarrest),
                             p_juv_fel_count=ifelse(p_juv_fel_count>2,2,p_juv_fel_count),
                             p_felassault_arrest=ifelse(p_felassault_arrest>3,3,p_felassault_arrest),
                             p_misdemassault_arrest=ifelse(p_misdemassault_arrest>3,3,
                                                           p_misdemassault_arrest),
                             p_murder_arrest=ifelse(p_murder_arrest>3,3,p_murder_arrest),
                             p_famviol_arrest=ifelse(p_famviol_arrest>3,3,p_famviol_arrest),
                             p_sex_arrest=ifelse(p_sex_arrest>3,3,p_sex_arrest),
                             p_weapons_arrest=ifelse(p_weapons_arrest>3,3,p_weapons_arrest),
                             total_fail_appear=ifelse(total_fail_appear>5,5,total_fail_appear)
                             )
```

